Master thesis problem statement: Keyword search over heterogeneous sources

### 2012-10-19 doc/thesis/latex/report_sept.tex
final version sept

Using a highly structured language like SQL is problematic because users need to know not only the language but also where to find the information and also lots of technical details like schema. An enterprise information integration system based on simple structured queries is already in place. Various improvements including: adding support for more complex queries and for less restricted keyword search, improvements to system's usability and performance still have to be researched.

>>>>

Using a highly structured language like SQL is problematic because users need to know not only the language but also where to find the information and also lots of technical details like schema. An enterprise information integration system based on simple structured queries is already in place. Various improvements  still have to be researched: adding support for more complex queries and for less restricted keyword search, improvements to system's usability and performance.
